Code to generate the figures needed in 'The influence of small reservoirs on

### 2022-07-02 R/Figures_code/paper_figures.Rmd
name change folder DNR

---
title: Code to generate the figures needed in 'The influence of small reservoirs on
  hydrological drought propagation in space and time'
author: "Paolo Colombo"
date: "08/05/2022"
output:
  html_document: default
  pdf_document: default
---

@@

Set the working directory and load general libraries and custom functions.
```{r, setwd, include = FALSE}
knitr::opts_knit$set(root.dir = "C:/Directory_thesis_codes")
```

@@

# Figure generation
## Figure 1
Map of the study area localization on the left. Centralized reservoirs visualization and density representation of the DRN on the right.
Made in QGIS for now. A code can be written by loading the shapefiles used there.

## Figure 2
Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al., 2022.
![Drought Cycle Analysis quadrant representation](C:/Directory_thesis_codes/Figures and tables/DCA_wheel_update.jpg)

@@

```{r figure 6}
setwd("C:/Directory_thesis_codes")
source("./R/Libraries/Libraries.R")
source("./R/Libraries/Functions.R")

DCA_real <- list.load("./Data/DCA/DCA_real.RData")
DCA_noH <- list.load("./Data/DCA/DCA_noH.RData")
DCA_obs <- list.load("./Data/DCA/DCA_obs.RData")
DCA_SR <- list.load("./Data/DCA/DCA_SR.RData")
DCA_N <- list.load("./Data/DCA/DCA_N.RData")

rename_scenarios = function(df){
  #df BEFORE reshape::melt!
  names(df)[names(df) == "Real"] <- "AR"
  names(df)[names(df) == "noHDNR"] <- "LR"
  return(df)
}

#Meteorological drought periods
#Based on Marengo et al., 2016
date_ranges_Marengo <- data.frame(
  from = as.Date(c("1981-01-01", "1982-01-01", "1992-01-01", "1997-01-01", "2001-01-01", "2005-01-01", "2007-01-01", "2010-01-01")),
  to = as.Date(c("1981-12-01", "1983-12-01", "1993-12-01", "1998-12-01", "2002-12-01", "2005-12-01", "2007-12-01", "2018-12-01"))
)
#Based on SPI
# negSPI <- DCA_real$Banabuiu$date[DCA_real$Banabuiu$PI < 0]
# negSPI
date_ranges_SPI <- data.frame(
  from = as.Date(c("1980-12-01", "1987-05-01", "1992-05-01", "1997-05-01", "2001-02-01", "2005-02-01", "2010-05-01", "2012-05-01", "2014-06-01")),
  to = as.Date(c("1984-03-01", "1988-04-01", "1994-04-01", "1999-12-01", "2002-02-01", "2005-12-01", "2010-12-01", "2014-01-01", "2018-12-01"))
)

#Arrojado Lisboa
df <- data.frame(date = DCA_real[['156']]$date, Real = DCA_real[['156']]$WSI, noHDNR = DCA_noH[['156']]$WSI)
plot_df_interactive(df)

df <- rename_scenarios(df)
df <- reshape2::melt(df, id.vars = 'date', variable.name = 'Scenario')

date_ranges <- date_ranges_SPI

p <- ggplot() +
  #Add the drought rectangles
  geom_rect(data = date_ranges, aes(xmin = from, xmax = to, ymin = -Inf, ymax = Inf), alpha = 0.4) +
  #Add the VD lines
  geom_line(data = df, aes(x = date, y = value, linetype = Scenario), alpha = 0.5, size = 1.25) +
  #VD = 0 line
  geom_hline(yintercept = 0, color = 'tomato2', linetype = "dashed", size = 1, alpha = 0.8) +
  #geom_text(aes(as.Date("1985-01-01"), 0, label = "VD = 0", vjust = -1, hjust = 0)) +
  scale_y_continuous(name = 'Volume Deviation (VD)', limits = c(-1, 1)) +
  scale_x_date(name = 'Date', date_breaks = "2 years", date_labels = '%Y', limits = as.Date(c("1980-01-01", "2018-12-01")), expand = c(0,0)) +
  theme(axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 20),
        axis.title = element_text(size = 22),
        legend.title = element_text(size = 20),
        legend.text = element_text(size = 18),
        legend.position = "bottom")
  #scale_color_manual(values = c("royalblue3", "steelblue"))
  #scale_color_manual(values = c("salmon1", "royalblue"))

print(p)
plot.save(p, width = 1280, height = 657, filename = "./Plots/vd_ARLR_present.png")

@@

plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_8a.png")
```

>>>>

---
title: Code to generate the figures needed in 'The influence of small reservoirs on
  hydrological drought propagation in space and time'
author: "Paolo Colombo"
date: "08/05/2022"
output:
  html_document: 
    fig_width: 10
    fig_height: 7
  pdf_document: default
editor_options: 
  chunk_output_type: inline
---

@@

Set the working directory and load general libraries and custom functions.

```{r, setwd, include = FALSE}
knitr::opts_knit$set(root.dir = "C:/Directory_thesis_codes")
```

@@

# Figure generation

## Figure 1

Map of the study area localization on the left. Centralized reservoirs visualization and density representation of the DRN on the right. Made in QGIS utilizing the shapefiles and rasters found in ./Data/DNR and ./Data/Shapefile. ![Study area framing. North-East Brazil, Ceará and Banabuiú catchment on the left. On the right, centralized reservoirs location and storage capacity, overlayed to DRN's density in the Banabuiú basin.](C:/Directory_thesis_codes/Figures%20and%20tables/paper/Figure_1.png)

## Figure 2

Graphical representation of the Drought Cycle Analysis, taken from Ribeiro Neto et al., 2022. ![Graphical representation of the Drought Cycle Analysis, from Ribeiro Neto et al. (2022). WSI: Water Scarcity Index, PI: Precipitation Index.](C:/Directory_thesis_codes/Figures%20and%20tables/paper/Figure%202.jpg){width="682"}

@@

```{r figure 6}

@@

# plot.save(p, width = 1920, height = 1080, filename = "./Figures and tables/paper/Figure_8a.png")
```
